\setVersion{1.6}
\setDate{2008/03/17}

\begin{Name}{1}{gluplot}{Alexei Soloviev}{The Gluplot Plotting Package}{The Gluplot Plotting Package}

\Prog{Gluplot} is a data plotting package. It was originally intended 
both as graphical library and as standalone program which would 
allow scientists and students to visualize data. 
(The "GLU" in gluplot means that it is OpenGL/GLU/glut based.) 
Gluplot handles both curves (2D) and surfaces (3D). For 2D plots, 
there are many plot styles, including lines, points, lines with 
points, error bars and impulses. Surfaces are plotted as a color 
map on the x-y plane. 
Gluplot supplies both linear and logarithmic axes. Moreover, 
any other axis distortion is available using gluplot library. 
Axis scale and also many other settings are changeable by gluplot 
command-line options or by menu items and hot-keys after it runs. 
After all, gluplot supports high quality plot output to PostScript (PS), 
Encapsulated PostScript (EPS) and Portable Document Format (PDF) files. 
\end{Name}


\section{SYNOPSIS}
%%%%%%%%%%%%%%%%%%

\Prog{gluplot}
\oOpt{-x}
\oOpt{-y}
\oOpt{-z}
\oOpt{-t}
\oOpt{-g}
\oOpt{-k}
\oOpt{-b}
\oOptArg{-p}{ name}
\oOpt{-n}
\oOptArg{-f}{ name}
\oOptArg{-c}{ name}
\oOptArg{-u}{ string}
\oOptArg{-w}{ string}
\oOptArg{-s}{ string}
\oOpt{-3}
\oOpt{-v}
\oOptArg{-a}{ value}
\oOptArg{-o}{ file}
\Arg{file}

\Prog{gluplot}
\oOpt{-h}
\oOpt{-V}


\section{OPTIONS}
%%%%%%%%%%%%%%%%%

\subsection{COMMON OPTIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{Description}

\item[\Opt{-x}, \Opt{--xlog}] set logarithmic scale for x-axis [linear]
\item[\Opt{-y}, \Opt{--ylog}] set logarithmic scale for y-axis [linear]
\item[\Opt{-z}, \Opt{--zlog}] set logarithmic scale for z-axis [linear]
\item[\Opt{-t}, \Opt{--no-ticks}] hide axis ticks [no]
\item[\Opt{-g}, \Opt{--grid}] show grid [no]
\item[\Opt{-k}, \Opt{--key}] show palette key [no]
\item[\Opt{-b}, \Opt{--black}] set background black [white]
\item[\Opt{-p}, \OptArg{--palette}{ name}]  set color palette [rainbow]
\item[\Opt{-n}, \Opt{--negative}] invert palette [no]
\item[\Opt{-f}, \OptArg{--font}{ name}] set labels font [helvetica-12]
\item[\Opt{-c}, \OptArg{--clip}{ name}] set clipping plane [none]

\end{Description}

\subsection{PLOT OPTIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{Description}

\item[\Opt{-u}, \OptArg{--using}{ string}] set columns in file for plot [1:2]
\item[\Opt{-w}, \OptArg{--with}{ string}] set plot style [lines]
\item[\Opt{-s}, \OptArg{--slice }{ string}] set lines in file for plot (from:to:stride) [all]
\item[\Opt{-3}, \Opt{--3D}] perform 3D plot [no]
\item[\Opt{-v}, \Opt{--volume}] show volume in 3D plot [surface]
\item[\Opt{-a}, \OptArg{--alpha }{ value}] set surface transparency [1.0]

\end{Description}

\subsection{OUTPUT OPTIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{Description}

\item[\Opt{-o}, \OptArg{--output}{ file}] output plot to file in EPS format [GLUT window]

\end{Description}


\subsection{HELP OPTIONS}
%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{Description}

\item[\Opt{-h}, \Opt{--help }] display this help and exit
\item[\Opt{-V}, \Opt{--version}] display version information and exit

\end{Description}


\LatexManEnd
